### 2017-02-01 local-capability-machine.tex
Added missing TODOs

\begin{lemma}[Revoke temporary memory satisfaction]
  \label{lem:priv-mono-like}
  \begin{align*}
    &      \forall \hs, n, W, W' \ldotp \\
    & \quad  \heapSat[\hs]{n}{W} \Rightarrow\\
    & \qquad \exists \hs', \hs_r \ldotp \\
    & \qquad \quad \hs = \hs' \uplus \hs_r \land \heapSat[\hs']{n}{\wrev{W}}
  \end{align*}
\end{lemma}

\begin{lemma}[Revoke temporary memory satisfaction 2]
  \label{lem:priv-mono-like2}
  \begin{align*}
    & \forall \ms, n, W, R : \activeReg{W} \fun \MemSegments  \ldotp \\
    & \quad \memSatPar{\ms}{W}{P} \Rightarrow \\
    & \qquad \exists \ms', \ms_r\ldotp \\
    & \qquad \quad \ms = \ms' \uplus \ms_r \land \\
    & \qquad \quad \memSatPar{\ms'}{\wrev{W}}{P|_{\dom(\erase{W}{\perma})}} \land \\
    & \qquad \quad \ms_r = \biguplus_{r \in \erase{W}{\temp}} P(r) \land \\
    & \qquad \quad \ms' = \biguplus_{r \in \erase{W}{\perma}} P(r)
  \end{align*}
\end{lemma}

\begin{lemma}[Revoke temporary memory with stack]
  \label{lem:revoke-temp-stack}
  \begin{align*}
    & \forall n, \ms, W, \reg, r_\stk,\gl,\start,\addrend,\addr \ldotp\\
    & \quad \memSat{\ms}{W} \land \npair{\reg} \in \stdrr(W) \land \\
    & \quad \reg(r_\stk) = ((\rwlx,\gl),\start,\addrend,\addr) \land b \leq e \\
    & \qquad \exists \ms', \ms_r \ldotp \\
    & \qquad \quad \memSat{\ms }{\revokeTemp{W}} \land \ms = \ms' \uplus \ms_r
  \end{align*}
\end{lemma}

\begin{lemma}[Disjoint memory satisfaction]
  \label{lem:disj-mem-sat}
  \begin{align*}
    & \forall n \ldotp \forall \ms, \ms', \ms'' \ldotp \forall W, W', W'' \ldotp\\
    & \quad \ms'' = \ms \uplus \ms' \land W'' = W \uplus W' \land \memSat{\ms}{W} \land \memSat{\ms'}{W'} \Rightarrow \\
    & \qquad \heapSat[\ms \uplus \ms' ]{n}{W \uplus W'}
  \end{align*}
\end{lemma}

\begin{lemma}[Memory satisfaction and static regions]
  \label{lem:mem-sat-static}
  \[
    \memSat{\ms}{[i \mapsto \iota^\sta(v,\ms)]}
  \]
\end{lemma}

\begin{lemma}[Data only memory and standard regions]
  \label{lem:mem-sat-data-only-std-regions}
  If
  \begin{itemize}
  \item $\forall \addr \in \dom(\ms)\ldotp \ms(a) \in \nats$
  \item $\iota \in \{\iota^\pwl,\iota^\nwl,\iota^{\nwl,p} \}$
  \end{itemize}
  then
  \[
    \memSat{\ms}{[i \mapsto \iota^\pwl(\dom(\ms))]}
  \]
\end{lemma}

@@

\begin{lemma}
  For all $W$, $W'$, and $W''$
  \begin{itemize}
  \item $W' \futurewk W \Rightarrow W' \futurestr W$
  \item $\wrev{W} \futurestr W$
  \end{itemize}
  Combined with transitivity of $\futurestr$, the above gives us:
  \begin{itemize}
  \item $W'' \futurestr W' \land W' \futurewk W \Rightarrow W'' \futurestr W$
  \item $W'' \futurewk W' \land W' \futurestr W \Rightarrow W'' \futurestr W$
  \end{itemize}
\end{lemma}

>>>>

\begin{lemma}[Revoke temporary memory satisfaction]
  \label{lem:priv-mono-like}
  \begin{align*}
    &      \forall \hs, n, W, W' \ldotp \\
    & \quad  \heapSat[\hs]{n}{W} \Rightarrow\\
    & \qquad \exists \hs', \hs_r \ldotp \\
    & \qquad \quad \hs = \hs' \uplus \hs_r \land \heapSat[\hs']{n}{\wrev{W}}
  \end{align*}
\end{lemma}
\begin{proof}[Proof of Lemma~\ref{lem:priv-mono-like}]
  % TODO
\end{proof}

\begin{lemma}[Revoke temporary memory satisfaction 2]
  \label{lem:priv-mono-like2}
  \begin{align*}
    & \forall \ms, n, W, R : \activeReg{W} \fun \MemSegments  \ldotp \\
    & \quad \memSatPar{\ms}{W}{P} \Rightarrow \\
    & \qquad \exists \ms', \ms_r\ldotp \\
    & \qquad \quad \ms = \ms' \uplus \ms_r \land \\
    & \qquad \quad \memSatPar{\ms'}{\wrev{W}}{P|_{\dom(\erase{W}{\perma})}} \land \\
    & \qquad \quad \ms_r = \biguplus_{r \in \erase{W}{\temp}} P(r) \land \\
    & \qquad \quad \ms' = \biguplus_{r \in \erase{W}{\perma}} P(r)
  \end{align*}
\end{lemma}
\begin{proof}[Proof of Lemma~\ref{lem:priv-mono-like2}]
  % TODO
\end{proof}

\begin{lemma}[Revoke temporary memory with stack]
  \label{lem:revoke-temp-stack}
  \begin{align*}
    & \forall n, \ms, W, \reg, r_\stk,\gl,\start,\addrend,\addr \ldotp\\
    & \quad \memSat{\ms}{W} \land \npair{\reg} \in \stdrr(W) \land \\
    & \quad \reg(r_\stk) = ((\rwlx,\gl),\start,\addrend,\addr) \land b \leq e \\
    & \qquad \exists \ms', \ms_r \ldotp \\
    & \qquad \quad \memSat{\ms }{\revokeTemp{W}} \land \ms = \ms' \uplus \ms_r
  \end{align*}
\end{lemma}
\begin{proof}[lem:revoke-temp-stack]
  % TODO
\end{proof}

\begin{lemma}[Disjoint memory satisfaction]
  \label{lem:disj-mem-sat}
  \begin{align*}
    & \forall n \ldotp \forall \ms, \ms', \ms'' \ldotp \forall W, W', W'' \ldotp\\
    & \quad \ms'' = \ms \uplus \ms' \land W'' = W \uplus W' \land \memSat{\ms}{W} \land \memSat{\ms'}{W'} \Rightarrow \\
    & \qquad \heapSat[\ms \uplus \ms' ]{n}{W \uplus W'}
  \end{align*}
\end{lemma}
\begin{proof}[Proof of Lemma~\ref{lem:disj-mem-sat}]
  % TODO
\end{proof}

\begin{lemma}[Memory satisfaction and static regions]
  \label{lem:mem-sat-static}
  \[
    \memSat{\ms}{[i \mapsto \iota^\sta(v,\ms)]}
  \]
\end{lemma}
\begin{proof}[Proof of Lemma~\ref{lem:mem-sat-static}]
  % TODO
\end{proof}

\begin{lemma}[Data only memory and standard regions]
  \label{lem:mem-sat-data-only-std-regions}
  If
  \begin{itemize}
  \item $\forall \addr \in \dom(\ms)\ldotp \ms(a) \in \nats$
  \item $\iota \in \{\iota^\pwl,\iota^\nwl,\iota^{\nwl,p} \}$
  \end{itemize}
  then
  \[
    \memSat{\ms}{[i \mapsto \iota^\pwl(\dom(\ms))]}
  \]
\end{lemma}
\begin{proof}[Proof of Lemma~\ref{lem:mem-sat-data-only-std-regions}]
  % TODO
\end{proof}

@@

\begin{lemma}[World private future world of revoked world]
  \label{lem:rt-w-priv-future-w}
  \[
    \forall W \ldotp \wrev{W} \futurestr W
  \]
\end{lemma}
\begin{proof}[Proof of Lemma~\ref{lem:rt-w-priv-future-w}]
  % TODO
\end{proof}

\begin{lemma}[Public future world relation included in private future world relation]
  \label{lem:future-pub-impl-future-priv}
  \[
   W' \futurewk W \Rightarrow W' \futurestr W
  \]
\end{lemma}
\begin{proof}[Proof of Lemma~\ref{lem:future-pub-impl-future-priv}]
  % TODO
\end{proof}

\begin{lemma}[Transitivity proberties between private and public future worlds]
\[
  W'' \futurestr W' \land W' \futurewk W \Rightarrow W'' \futurestr W
\]
and
\[
  W'' \futurewk W' \land W' \futurestr W \Rightarrow W'' \futurestr W
\]
\end{lemma}
\begin{proof}[Proof of Lemma~\ref{lem:future-priv-pub-trans}]
  % TODO
\end{proof}
